They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-12 paper.tex
Paper: polarvector edits

The implementation details of PolarVector's conversion functions are fairly trivially derived from math, but it should be noted that all Cartesian components are encoded as Vector3 components as the game takes place on the X-Z plane (see Figure 6).

>>>>

The implementation details of PolarVector's conversion functions are fairly
trivially derived from math, but it should be noted that all Cartesian
components are encoded as two dimensions of a \texttt{Vector3} as the game takes
place on the X-Z plane (see Figure 6).
